Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-11-29 article.qmd
Add screenshots

::: {#fig-constant layout-nrow=2}
```{python}
# | echo: false
from poincare import Constant, Parameter, assign

```{python}
class Model(System):
    c: Constant = assign(default=1, constant=True)
    x: Variable = initial(default=c)
    y: Variable = initial(default=c)

```{python}
class BadModel(System):
    p: Parameter = assign(default=1)
    z: Variable = initial(default=p)  # type error

Constant and Parameter allow to connect initial conditions and equations, respectively.
Using Parameters as initial conditions raises an error,
and can be flagged by static type checkers.
:::

>>>>

::: {#fig-constant layout-nrow=1}

::: {#fig-parameter layout-nrow=2}
![](src/ide/constant.png)

![](src/ide/type_error.png)

`Constant` are assigned with `assign(..., constant=True)` and allow to link `Variable`s initial conditions,
while trying to use a `Parameter` instead is flagged as type errors (red underlining).
:::

::: {#fig-composition layout-nrow=1}
![](src/ide/composition_tooltip.png)

A tooltip is shown when composing models,
which show the expected variables and their default values.
The IDE highlights mismatched types (`my_var` is `Variable` and `c` must be a number or a `Constant`)
and wrong names (`z` is not a name in `Model`).
:::

Screenshots of Visual Studio Code showing tooltips and highlighted type errors.
:::
